%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ganesh Mahata Resume
% Version 2.0
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper]{article}

%-----------------------------------------------------------
% Packages
%-----------------------------------------------------------

\usepackage[left=0.60in,right=0.60in,top=0.55in,bottom=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{setspace}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Colors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\definecolor{primary}{RGB}{15,55,110}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section Formatting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\titleformat{\section}
{\large\bfseries\color{primary}}
{}{0em}{}[\titlerule]

\titlespacing{\section}
{0pt}
{6pt}
{4pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\resumeItem}[1]{
\item\small{#1}
}

\newcommand{\resumeProject}[4]{
\textbf{#1}
\hfill
{\small #2}

\textit{#3}

#4

\vspace{6pt}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}

{\Huge \textbf{GANESH MAHATA}}

\vspace{4pt}

B.Tech Undergraduate | Biotechnology

Indian Institute of Technology Delhi

\vspace{4pt}

\faEnvelope\
\href{mailto:iitd.mahata@gmail.com}{iitd.mahata@gmail.com}
\hspace{10pt}

\faGithub\
\href{https://github.com/GaneshMahata}{github.com/GaneshMahata}

\hspace{10pt}

\faGlobe\
\href{https://ganeshmahata.github.io}
{ganeshmahata.github.io}

\hspace{10pt}

\faLinkedin\
LinkedIn

\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Professional Summary}

Biotechnology undergraduate at the Indian Institute of Technology Delhi with strong interests in embedded systems, Internet of Things (IoT), web development, and AI-assisted engineering. Passionate about designing practical software and hardware solutions that integrate modern technologies with real-world applications. Experienced in developing responsive websites, cloud-connected embedded systems, and technical automation projects while continuously exploring interdisciplinary engineering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}

\begin{tabularx}{\linewidth}{|l|X|c|c|}
\hline

\textbf{Year}
&
\textbf{Institute}
&
\textbf{Degree}
&
\textbf{CGPA/Marks}

\\
\hline

2023--Present
&
Indian Institute of Technology Delhi
&
B.Tech Biotechnology
&
5.62

\\
\hline

2022
&
Jawahar Navodaya Vidyalaya, Bankura
&
Class XII (CBSE)
&
76.4\%

\\
\hline

2020
&
Jawahar Navodaya Vidyalaya, Bankura
&
Class X (CBSE)
&
80\%

\\
\hline

\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Technical Skills}

\textbf{Programming Languages}

Python, C, C++, HTML5, CSS3, JavaScript, SQL

\vspace{3pt}

\textbf{Web Development}

Responsive Web Design, GitHub Pages, Frontend Development

\vspace{3pt}

\textbf{Embedded Systems}

ESP32, ESP8266, Arduino, NodeMCU, RFID, OLED Displays, IoT Sensors

\vspace{3pt}

\textbf{Databases}

Firebase, Supabase, PostgreSQL (Learning)

\vspace{3pt}

\textbf{Developer Tools}

Git, GitHub, VS Code, Grafana, LTspice, SimulIDE, Canva

\vspace{3pt}

\textbf{Areas of Interest}

Artificial Intelligence,
Internet of Things,
Embedded Systems,
Automation,
Biotechnology,
Software Engineering,
Research,
Open Source Development

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Projects}

\resumeProject
{Student Management System}
{2026}
{Full Stack Web Application}
{
\begin{itemize}[leftmargin=*]

\resumeItem{Designed and developed a modern student management portal with responsive user interface and modular architecture.}

\resumeItem{Implemented secure authentication, student record management, and role-based administrative features.}

\resumeItem{Focused on scalable design, clean navigation, and maintainable project structure using modern web technologies.}

\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeProject
{Department Website}
{2026}
{Frontend Development}
{
\begin{itemize}[leftmargin=*]

\resumeItem{Developed a responsive departmental website featuring semester-wise course resources and academic information.}

\resumeItem{Improved usability through intuitive navigation, mobile-friendly layouts, and optimized performance.}

\resumeItem{Maintained project using Git and GitHub with structured version control workflow.}

\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeProject
{ESP32 IoT Monitoring System}
{2026}
{Embedded Systems}
{
\begin{itemize}[leftmargin=*]

\resumeItem{Built an IoT monitoring platform using ESP32 for real-time sensor data acquisition and cloud communication.}

\resumeItem{Integrated wireless connectivity and live monitoring concepts for remote device management.}

\resumeItem{Explored scalable embedded system architecture for future automation applications.}

\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeProject
{Grafana Dashboard Integration}
{2026}
{Data Visualization}
{
\begin{itemize}[leftmargin=*]

\resumeItem{Designed interactive dashboards to visualize sensor and monitoring data using Grafana.}

\resumeItem{Configured data sources and optimized dashboard layouts for clear presentation of real-time information.}

\resumeItem{Investigated cloud-based monitoring workflows for engineering applications.}

\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeProject
{Personal Portfolio Website}
{2026}
{Web Development}
{
\begin{itemize}[leftmargin=*]

\resumeItem{Designed and developed a responsive personal portfolio showcasing projects, technical skills, achievements, and resume.}

\resumeItem{Implemented dark/light theme, responsive layouts, and modern UI components for enhanced user experience.}

\resumeItem{Optimized the website for GitHub Pages deployment with fast loading and clean architecture.}

\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Research Interests}

Artificial Intelligence \textbullet\
Embedded Systems \textbullet\
Internet of Things \textbullet\
Biotechnology \textbullet\
Automation \textbullet\
Biomedical Devices \textbullet\
Software Engineering \textbullet\
Open Source Technologies

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Achievements}

\begin{itemize}[leftmargin=*]

\resumeItem{Qualified Joint Entrance Examination (JEE) and secured admission to the Indian Institute of Technology Delhi.}

\resumeItem{Recipient of multiple merit-based scholarship opportunities during academic journey.}

\resumeItem{Continuously expanding practical expertise through self-driven engineering and software development projects.}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Positions of Responsibility
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Positions of Responsibility}

\textbf{RDV Security Team}

Indian Institute of Technology Delhi

\begin{itemize}[leftmargin=*]

\resumeItem{Contributed to crowd management and event operations during IIT Delhi's annual cultural festival.}

\resumeItem{Worked collaboratively with volunteers to ensure smooth coordination and safe execution of large-scale events.}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Extra Curricular Activities}

\begin{itemize}[leftmargin=*]

\resumeItem{Actively participate in athletics and sports activities at IIT Delhi.}

\resumeItem{Strong interest in electronics prototyping, embedded systems, and open-source software development.}

\resumeItem{Continuously explore emerging technologies through independent learning and hands-on projects.}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Languages}

English \hspace{12pt}
Hindi \hspace{12pt}
Bengali

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Declaration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{6pt}

\begin{center}

\rule{0.45\linewidth}{0.4pt}

\vspace{2pt}

{\small
Last Updated: July 2026
}

\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}